---
title: Tuango - RFM Analysis for Mobile App Push Messaging on the post roll-out data
output: html_document
---

* Name:
* GitLab id:

```{r r_setup, include = FALSE}
## initial settings
knitr::opts_chunk$set(
  comment = NA,
  echo = TRUE,
  error = TRUE,
  cache = FALSE,
  message = FALSE,
  dpi = 96,
  warning = FALSE
)

## width to use when printing tables etc.
options(
  width = 250,
  scipen = 100,
  max.print = 5000,
  stringsAsFactors = FALSE
)

## make all required libraries available by loading radiant package if needed
if (!exists("r_environment")) library(radiant)
```

<style>
.btn, .form-control, pre, code, pre code {
  border-radius: 4px;
}
.table {
  width: auto;
}
ul, ol {
  padding-left: 18px;
}
code, pre, pre code {
  overflow: auto;
  white-space: pre;
  word-wrap: normal;
}
code {
  color: #c7254e;
  background-color: #f9f2f4;
}
pre {
  background-color: #ffffff;
}
</style>

## Setup

Please complete this Rmarkdown document by answering question 14 in `tuango.pdf` on Canvas (week4/). The code block below loads the data you need for this second Rmarkdown file. Create an HTML file with all your results and answers and push both the Rmarkdown and HTML file to GitLab when you are done. All results MUST be reproducible (i.e., the TA and I must be able to recreate the Notebook/HTML from the Rmarkdown file without changes or errors).

```{r}
## loading the data - this dataset must NOT be changed
tuango_post <- readr::read_rds("data/tuango_post.rds")
```

## Question answers

### Question 14
```{r}
library(radiant)

register("tuango_post")
## create new variable(s)
tuango_post <- mutate(tuango_post, rec_iq = xtile(recency, 5))
## create new variable(s)
tuango_post <- mutate(tuango_post, freq_iq = xtile(frequency, 5, rev = TRUE))
## create new variable(s)
tuango_post <- mutate(tuango_post, mon_iq = xtile(monetary, 5, rev = TRUE))
## create new variable(s)
tuango_post <- mutate(tuango_post, rfm_iq = paste0(rec_iq, freq_iq, mon_iq))
## create new variable(s)
tuango_post <- group_by(tuango_post, rec_iq) %>%
  mutate(freq_sq = xtile(frequency, 5, rev = TRUE)) %>%
  ungroup()
## create new variable(s)
tuango_post <- group_by(tuango_post, rec_iq, freq_sq) %>%
  mutate(mon_sq = xtile(monetary, 5, rev = TRUE)) %>%
  ungroup()
tuango_post <- mutate(tuango_post, rfm_sq = paste0(rec_iq, freq_sq, mon_sq))

rev <- mean(data.matrix(tuango_post[tuango_post$buyer == 'yes' & tuango_post$training == 1, "ordersize"]))
breakeven <- 2.5/(rev*0.5)

temp <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_iq) %>%
  summarise(mailto_iq = mean(buyer == "yes") > breakeven) %>%
  ungroup()
tuango_post <- tuango_post %>%
  left_join(temp, by = c("rfm_iq" = "rfm_iq"))
## create new variable(s)
temp <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_sq) %>%
  summarise(mailto_sq = mean(buyer == "yes") > breakeven) %>%
  ungroup()
tuango_post <- tuango_post %>%
  left_join(temp, by = c("rfm_sq" = "rfm_sq"))

perf_calc <- function(x){
  tuango_post %>%
    filter(training == 0, tuango_post[, x] == TRUE) %>%
    summarise(
      population = n(),
      expenditure = population * 2.5,
      rep_rate = mean(buyer == "yes"),
      #nr_resp = nr_mail * rep_rate,
      # profit = mean(ordersize) * nr_resp - mail_cost,
      profit = 0.5 * sum(ordersize) - expenditure,
      ROME = profit / expenditure,
    )
}

profit_iq <- perf_calc('mailto_iq')[4]
print(profit_iq)
ROME_iq <- perf_calc('mailto_iq')[5]
print(ROME_iq)
profit_sq <- perf_calc('mailto_sq')[4]
print(profit_sq)
ROME_sq <- perf_calc('mailto_sq')[5]
print(ROME_sq)

Breakeven <- tuango_post %>%
  filter(buyer == "yes" & training == 1) %>%
  group_by(rfm_sq) %>%
  summarise(breakeven_each = 2.5 / (mean(ordersize)*0.5)) %>%
  ungroup()

Breakeven <- tuango_post %>%
  distinct(rfm_sq) %>%
  left_join(Breakeven, by=c("rfm_sq"="rfm_sq"))

tuango_post <- tuango_post %>%
  left_join(Breakeven, by = "rfm_sq")

tuango_post$breakeven_each <- tuango_post$breakeven_each %>% replace_na(1)

temp <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_sq) %>%
  summarise(mailto10_sq= mean(buyer == "yes") > mean(breakeven_each)) %>%
  ungroup()
tuango_post <- tuango_post %>%
  left_join(temp, by = c("rfm_sq" = "rfm_sq"))

profit_sq_cell <- perf_calc('mailto10_sq')[4]
ROME_sq_cell <- perf_calc('mailto10_sq')[5]


temp <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_iq) %>%
  summarise(mailto_lbiq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > breakeven) %>%
  ungroup()
tuango_post <- tuango_post %>%
  left_join(temp, by = c("rfm_iq" = "rfm_iq"))
## create new variable(s)
temp <- tuango_post %>%
  filter(training == 1) %>%
  group_by(rfm_sq) %>%
  summarise(mailto_lbsq = (mean(buyer == "yes") - 1.64 * seprop(buyer == "yes")) > breakeven) %>%
  ungroup()
tuango_post <- tuango_post %>%
  left_join(temp, by = c("rfm_sq" = "rfm_sq"))

profit_lbiq <- perf_calc('mailto_lbiq')[4]
ROME_lbiq <- perf_calc('mailto_lbiq')[5]
profit_lbsq <- perf_calc('mailto_lbsq')[4]
ROME_lbsq <- perf_calc('mailto_lbsq')[5]

results <- tibble::tibble(
  name = c("Indep. RFM", "Seq. RFM", "Seq. RFM with each BE", "Indep. lb RFM", "Seq. lb RFM"),
  Profit = c(as.numeric(profit_iq), as.numeric(profit_sq), as.numeric(profit_sq_cell), as.numeric(profit_lbiq), as.numeric(profit_lbsq)),
  ROME = c(as.numeric(ROME_iq), as.numeric(ROME_sq), as.numeric(ROME_sq), as.numeric(ROME_lbiq), as.numeric(ROME_lbsq))) %>%
  mutate(name = factor(name, levels = name))

results %>%
  ggplot(aes(x = name, y = Profit)) + geom_bar(stat = "identity") + geom_text(aes(label = round(Profit, 2)), size = 3)

results %>%
  ggplot(aes(x = name, y = ROME)) + geom_bar(stat = "identity") + geom_text(aes(label = round(ROME, 2)), size = 3)


```


